More straightforward movement variable definitions

### 2024-02-07 scripts/01.1_categorizeMovement.qmd
made plots prettier

movement %>%
  pivot_longer(cols = c("mnDailyMnAlt", "meanDFD", "meanDMD", "meanDDT", "mnTort"),
               names_to = "measure", values_to = "value") %>%
  mutate(measure = fct_recode(measure,
                              "Daily mean altitude (seasonal avg)" = 
                                "mnDailyMnAlt",
                              "Daily flight time (seasonal avg)" = 
                                "meanDFD",
                              "Daily max displacement (seasonal avg)" = 
                                "meanDMD",
                              "Daily distance traveled (seasonal avg)" = 
                                "meanDDT",
                              "Tortuosity (seasonal avg)" = 
                                "mnTort")) %>%
  ggplot(aes(x = movement_pc1, y = value))+
  geom_point()+geom_smooth(method = "lm")+theme_minimal()+
  facet_wrap(~measure, labeller = labeller(measure = label_wrap_gen(30)))+
  ylab("Value (scaled)")+
  theme(legend.position = "none")
```

@@

roost_behavior %>%
  rename("Shannon roost diversity" = "shannon", "Unique roosts" = "uniqueRoosts", "Prop. nights roost-switching" = "propSwitch") %>%
  pivot_longer(cols = c("Shannon roost diversity", "Unique roosts", "Prop. nights roost-switching"),
               names_to = "measure", values_to = "value") %>%
  ggplot(aes(x = roost_pc1, y = value))+
  geom_point()+geom_smooth(method = "lm")+theme_minimal()+
  facet_wrap(~measure)+
  ylab("Value (scaled)")+
  theme(legend.position = "none")
```

@@

```{r}
#| message: false
#| warning: false
red %>%
  ggplot(aes(x = movement, y = roost_div))+
  geom_point(color = "purple")+ geom_smooth(method = "lm", col = "purple")+ theme_minimal()
```

@@

```{r}
#| message: false
#| warning: false
red %>%
  ggplot(aes(x = roost_div, y = space_use_log))+
  geom_point(color = "chartreuse3")+ geom_smooth(method = "lm", col = "chartreuse3")+ theme_minimal()
```

@@

```{r}
#| message: false
#| warning: false
red %>%
  ggplot(aes(x = space_use_log, y = movement))+
  geom_point(color = "orange2")+ geom_smooth(method = "lm", col = "orange2")+ theme_minimal()
```

@@

>>>>

movement %>%
  pivot_longer(cols = c("mnDailyMnAlt", "meanDFD", "meanDMD", "meanDDT", "mnTort"),
               names_to = "measure", values_to = "value") %>%
  mutate(measure = fct_recode(measure,
                              "Daily mean altitude (seasonal avg)" = 
                                "mnDailyMnAlt",
                              "Daily flight time (seasonal avg)" = 
                                "meanDFD",
                              "Daily max displacement (seasonal avg)" = 
                                "meanDMD",
                              "Daily distance traveled (seasonal avg)" = 
                                "meanDDT",
                              "Tortuosity (seasonal avg)" = 
                                "mnTort")) %>%
  ggplot(aes(x = movement_pc1, y = value))+
  geom_point()+geom_smooth(method = "lm")+theme_minimal()+
  facet_wrap(~measure, labeller = labeller(measure = label_wrap_gen(30)))+
  ylab("Value (scaled)")+
  theme(legend.position = "none",
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())
```

@@

roost_behavior %>%
  rename("Shannon roost diversity" = "shannon", "Unique roosts" = "uniqueRoosts", "Prop. nights roost-switching" = "propSwitch") %>%
  pivot_longer(cols = c("Shannon roost diversity", "Unique roosts", "Prop. nights roost-switching"),
               names_to = "measure", values_to = "value") %>%
  ggplot(aes(x = roost_pc1, y = value))+
  geom_point()+geom_smooth(method = "lm")+theme_minimal()+
  facet_wrap(~measure)+
  ylab("Value (scaled)")+
  theme(legend.position = "none",
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())
```

@@

```{r}
#| message: false
#| warning: false
cor <- round(cor(red$movement, red$roost_div), 2)
red %>%
  ggplot(aes(x = movement, y = roost_div))+
  geom_point(color = "purple")+ geom_smooth(method = "lm", col = "purple")+ theme_minimal()+
  ylab("Roost diversification")+
  xlab("Movement")+
  ggplot2::annotate(geom = "text", x = 4.5, y = -2, label = paste0("Correlation = ", cor))
```

@@

```{r}
#| message: false
#| warning: false
cor <- round(cor(red$roost_div, red$space_use_log), 2)
red %>%
  ggplot(aes(x = roost_div, y = space_use_log))+
  geom_point(color = "chartreuse3")+ geom_smooth(method = "lm", col = "chartreuse3")+ theme_minimal()+
  xlab("Roost diversification")+ ylab("Space use (log)")+
  ggplot2::annotate(geom = "text", x = 4, y = 11, label = paste0("Correlation = ", cor))
```

@@

```{r}
#| message: false
#| warning: false
cor <- round(cor(red$space_use_log, red$movement), 2)
red %>%
  ggplot(aes(x = space_use_log, y = movement))+
  geom_point(color = "orange2")+ geom_smooth(method = "lm", col = "orange2")+ theme_minimal()+
  xlab("Space use (log)") + ylab("Movement")+
  ggplot2::annotate(geom = "text", x = 14, y = -4.5, label = paste0("Correlation = ", cor))
```

@@

```{r}
#| warning: false
#| message: false
## TEMPORARY: FOR PRESENTATION
load(here::here("data", "derived", "cc.Rda"))
red %>%
  mutate(season = stringr::str_extract(seasonUnique, "[a-z]+")) %>%
  pivot_longer(cols = c("movement", "roost_div", "space_use_log"),
               names_to = "var", values_to = "value") %>%
  ggplot(aes(x = age, y = value, group = seasonUnique, col = season))+
  geom_point(alpha = 0.5) + geom_smooth(se = F)+
  theme_minimal()+
  xlab("Age")+
  facet_wrap(~var, scales = "free")+
  scale_color_manual(values = c(cc$breedingColor, cc$fallColor, cc$summerColor))+
  theme()
```
